Results

### 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@

[to be filled]

>>>>

[... WAHLVERHALTEN FEHLT NOCH ...]

@@

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model

``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  escape = FALSE,
  placement = "H")
```
